\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-26 coqimpl.tex

Note that, in our example, we include two
functors without arguments---this is due to a peculiarity of Coq's
"Include": uninstantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module.
For example, "b_7" requires a module of type "a_6". Inside module "A",
when "Include a_4" is done, we will have a field \mintinline{Coq}{a : nat}
inside the current surrounding "A". Then when we
\mintinline{Coq}{Include b_7} without specifying the module parameter,
Coq will try to find fields in the surrounding module (i.e., module
"A") to instantiate \mintinline{Coq}{self_A: a_6}. This is satisfied by
the \mintinline{Coq}{a : nat} that is included earlier.
The resulting compiled module is just like mundane Coq's module and 
thus maintains all the computational mechanism from Coq, fulfilling
requirements in \ref{chg:software-engineering}.\YZ{
  Do I understand correctly that an alternative to individually
  compiling family members to modules is to compile a family as a whole,
  but this alternative would not satisfy the "incremental type checking"
  or "instant feedback" requirement?
}\YZreply{
  Looks like individually compiling family members addresses not only
  this requirement, but also the "self vs. consistency" challenge.
}

@@

However, we later still need the concrete eliminator on "tm" for doing
exhaustiveness checking (as in \ref{chg:extensible-inductive-type}),
thus we will store the corresponding info somewhere.  Here we show one
exemplar extraction of the eliminator to \mintinline{Coq}{Set} as module
"tm_rec_425". This concrete eliminator will be used by our "FRecursor".
For example, in \cref{fig:plugin-example2}, "FRecursor" command will
feed Coq a module "v_33_34" for doing type-checking with specified
handlers (e.g. "neg_handler") during compilation---what it does is
basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.\YZ{
  Sounds like we can still claim the plugin is doing type checking.
  It's just that the checking is done by generating some Coq code and
  then having Coq check it.
}
Note that, at this point of the example,
"FRecursor" will only do type check. The compilation of "FRecursor" into
a component of the compiled module only happens when closing the whole
family, by inserting the following into the compiled module: 
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and
the (vanilla) inductive type in that compiled module. Thus a "FRecursor"
field is unlike other fields, even though it is exposed as a mundane
function for the following fields in the programming interface.\YZ{
  Why is this special treatment needed for compiling FRecursor?
}

>>>>

Note that, in our example, we include two
functors without arguments---this is due to a peculiarity of Coq's
"Include": uninstantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module.
For example, "b_7" requires a module of type "a_6". Inside module "A",
when "Include a_4" is done, we will have a field \mintinline{Coq}{a : nat}
inside the current surrounding "A". Then when we
\mintinline{Coq}{Include b_7} without specifying the module parameter,
Coq will try to find fields in the surrounding module (i.e., module
"A") to instantiate \mintinline{Coq}{self_A: a_6}. This is satisfied by
the \mintinline{Coq}{a : nat} that is included earlier.
The resulting compiled module is just like mundane Coq's module and 
thus maintains all the computational mechanism from Coq, fulfilling
requirements in \ref{chg:software-engineering}.\YZ{
  Do I understand correctly that an alternative to individually
  compiling family members to modules is to compile a family as a whole,
  but this alternative would not satisfy the "incremental type checking"
  or "instant feedback" requirement?
}\YZreply{
  Looks like individually compiling family members addresses not only
  this requirement, but also the "self vs. consistency" challenge.
}\EDJreply{Yes. Indivially compiling family member is to achieve both requirements}

@@

However, we later still need the concrete eliminator on "tm" for doing
exhaustiveness checking (as in \ref{chg:extensible-inductive-type}),
thus we will store the corresponding info somewhere.  Here we show one
exemplar extraction of the eliminator to \mintinline{Coq}{Set} as module
"tm_rec_425". This concrete eliminator will be used by our "FRecursor".
For example, in \cref{fig:plugin-example2}, "FRecursor" command will
feed Coq a module "v_33_34" for doing type-checking with specified
handlers (e.g. "neg_handler") during compilation---what it does is
basically
assert the existence of the recursor and apply to see if handlers can
pass the type checking by Coq.\YZ{
  Sounds like we can still claim the plugin is doing type checking.
  It's just that the checking is done by generating some Coq code and
  then having Coq check it.
}\EDJreply{Yes! If my phrasing doesn't make things clear (i.e. our plugin is doing typechecking),
feel free to change the phrasing for me}
Note that, at this point of the example,
"FRecursor" will only do type check. The compilation of "FRecursor" into
a component of the compiled module only happens when closing the whole
family, by inserting the following into the compiled module: 
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and
the (vanilla) inductive type in that compiled module. Thus a "FRecursor"
field is unlike other fields, even though it is exposed as a mundane
function for the following fields in the programming interface.\YZ{
  Why is this special treatment needed for compiling FRecursor?
}\EDJreply{because the non-special treatment cannot be applied to recursor --
  the non-special treatment will require the recursor to be *exported* at the interface}
